---
title: "First Knit"
author: "Sam Ibrahim"
date: "Aug 19, 2019"
output: 
  html_document:
    number_sections: true
    toc: true
---

### `r as.character(Sys.Date())`

```{r include=FALSE,echo=FALSE}
require(tidyverse)
if(!require("imager")) {install.packages("imager");require("imager")}

```

```{r echo=FALSE,out.width='100%'}
xx<-getwd()
Drive_ltr <- strtrim(xx,2)
yy <- str_glue("{Drive_ltr}\\AAA_Owner_Info\\My_photo.jpg")
my_pict <- load.image(yy)
plot(my_pict,axes=FALSE,main="I'm Confused")
```

# A Little Survey

Here are just a few questions so I can get to know you and so you can get practice submitting an assignment in Canvas.  For each question, insert your answer underneath. Make sure each answer is at the minimum a complete sentence with correctly spelled words and correct puncuation. Half the points in this assignment depend on your picture and name being correct!!  Be sure to put your photo in the AAA_Owner_Info folder and call it My_photo.jpg after first renaming the current one to Koala.jpg . 

##Where are you now?  
What row are you in, front,middle or back?  Do you usually choose a similiar row in other classes? What is the computer number where you are sitting?  How on a scale of 1 to 10 (1=low, 10=high) How you feel about periodic seat re-assignment, say how and why. Teams, have you ever worked on one in a class setting?  

###my answer     
 Currently I am sittibng in the back row on computer 40. No it actually depends on the empty seats and when I get to class if I am running late or early. I am indefferent about the periodic seat changes so lets say a 5, because its a good way to interact with other students. Yes i am and they are interesting to say the least. 
   
     


##Others and You?   
What name do you prefer to be called by your classmates and instructor, if your buddys call you something but you want me to call you something else - what would that be? 

###my answer     
 Sam works great for me, its easier. My freinds and family all call me Sammy but I feel only comforatble if I know the person calling me that. 
   
 




##Aspirations?   
What do you want to achieve in life?  What college subject do you think would be of the greatest interest to you? What degree or certificate are you trying to achieve?

###my answer     
  I wish top be a therapist that works with herbal medicine and esoteric modalities to help and nourish clients. the collgege subjects that I feel would interst me are psychology, anatomy, physiology, herbalogy(if they have them) and classes about other religions and healing techniques.I am trying to achieve a masters degree in psychology.
  
  




##Past adventures?  
Have you ever gone to foreign countries, if so which ones, if not Where might you go in the future?  Have you ever been in the military, if so which branch, if not which branch would you choose if you got drafted, and why?

###my answer     
  I have gone to Syria, and Mexico. I wish to go to more countires and see more of Syria. I have never been in the military but if I had to choose a brach I would choose the Medical team.
   
  




##Why are you taking Math 115?  
What grade do you need to attain in stats to not upset your future plans, What is your plan?
 

###my answer     
 I need to get an "A" or lowest a "B" in the class so I can get into the CSUN psychology program.    
   
 





##Homework Help and Getting around?  
On a scale of 1 to 10, where 1 is a total dummy (doesn't know a mouse from a keyboard) and 10 is a complete geek (knows computer stuff in and out) How do you rate yourself?  Do you have a computer you can use at home? If so, what kind is it (windows, Apple, Linux)? Do you have internet access at home?  
How do you get to class? Are there issues that limit when you can be at the college?Where and when did you attend high school?  Do you currently have a job?

###my answer   
  I can't scale myself because I am all over with cmputer stuff i understand something things but other things I am an idiot with. I dop have a computer at home I can use its a windows computer and yes we have internet access. I get to class by car, bike, walking. So far there is nothing limiting me from being at the cologe. I attended Palmdale Highschool and graduated 2010. I currently have three jobs. Might quit my weekend job depening on my classes.
  




